\documentclass{letter}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{fourier}
% \usepackage{mathptmx}


\begin{document}

\signature{Marius Peter}
\longindentation=0pt
\address{Marius Peter\\
  519 Landfair Ave\\
  Los Angeles CA 90024
}


\begin{letter}{Attn: Hiring Manager\\
    Boston Consulting Group\\
    515 South Flower Street, Suite 5100\\
    Los Angeles, CA 90071 USA
  }

  \opening{\vfill Dear Hiring Manager,}
  
  I am writing to explain how I became an invaluable member of my sales team during my previous role as assistant business analyst at Cosmo Tech.

  By the end of my employment at Cosmo Tech, I had contributed to securing initial funding from Airbus for a Model-Based System Engineering tool designed for the European aerospace sector.
  Airbus wanted better visibility in the \textit{Final Assembly Line} stage of the A320 Neo manufacturing, because the increased complexity of this new aircraft made it very difficult to evaluate the impact of an upstream delay on the final assembly duration.

  Following the initial contact with the Airbus team, I strived to understand their modeling workflow by downloading trial versions of the softwares they used (PolarSys Capella and SIMPROCESS), and modeling a typical \textit{FAL} environment;
  then, I repeated the same exercise using Cosmo's in-house tools, as well as a competitor's product (AnyLogic).

  During the next conference call with the Airbus team, I laid down the results of my benchmark and presented Cosmo's value propositon.
  I connected our product's features with the requirements Airbus had elicited earlier, and showcased how our product best met their needs.
  Airbus was thrilled by our efforts to understand their current workflow, and were rapidly convinced as to why they should buy Cosmo's solution over competiting products.

  This experience enabled me to better understand the end-to-end sales process, from lead generation till sale closure;
  to improve my listening skills during the requirements elicitation phase;
  and to further develop my understanding of Model-Based System Engineering in an industrial setting. 

  The results I outline above lead me to consider the role of consultant at the very intersection of my education, experiences and passions.

  \closing{Thank you for your consideration,}

\end{letter}

\end{document}
