\documentclass{letter}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{fourier}


\begin{document}


\signature{Marius Peter}
\longindentation=0pt
\address{Marius Peter\\
11090 Strathmore Dr\\
Los Angeles CA 90024
}


\begin{letter}{JetOptions Jet Charter\\
9465 Wilshire Blvd Suite 300\\
Beverly Hills CA 90212\\
\bigskip
\textbf{Subject:} JetOptions cover letter\\
\textbf{Position:} Entry-Level Sales Representative\\
}
\opening{\vfill~Dear Hiring Manager,}

The sales representative opportunity at JetOptions caught my attention because of the many skills I can transfer from my previous role as assistant business analyst.
By the end of my previous employment at Cosmo Tech, I had secured funding from Airbus for a Decision Support Software designed to optimize aircraft assembly planning.  

Following the initial contact with the Airbus team, I studied their planning workflow for the \emph{Final Assembly Line} segment of the A320neo manufacturing.
Then, I repeated the same exercise using Cosmo's in-house tools, as well as a competitor's product (\textit{AnyLogic}).

During the next conference call with Airbus, I presented my comparison of their current workflow, our solution, and that of \textit{AnyLogic}. 
I connected our software's features with the requirements that we had elicited earlier, and showcased how our product best met their needs.
Airbus was thrilled by our efforts to understand their current workflow, and were rapidly convinced to buy a license for Cosmo's solution.

% The successful sale resulted from carefully listening to my client's objectives, leading to a fruitful requirements elicitation process; I used my technical knowledge to elaborate a solution, but only once I had thoroughly understood both their needs and wants.
% My mentor praised the speed at which I created trust between our client and Cosmo Tech, and the high level of satisfaction on their end after we presented our proposal.

The results I outline above lead me to consider a sales role at JetOptions at the very intersection of my experiences, education and passions.
Adding to this, I speak English and French fluently, am proficient in German, and can hold a phatic conversation in Mandarin Chinese in a business setting. 

If JetOptions is seeking a sales representative who displays commitment to his client's needs every single day, has a proven ability for sales, and is capable of evolving in a multi-lingual customer environment, I am the person that you need.

\closing{Thank you for your consideration,}

\encl{Résumé}

\end{letter}

\end{document}
