% Included packages
\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage{hyperref}

\pagenumbering{gobble}
\setstretch{1.15}
\newgeometry{margin=1in}


\begin{document}

\noindent Marius Peter \hfill \today\\
11090 Strathmore Dr\\
Los Angeles CA 90024\\
818 284 3757\\
\href{mailto:mpeter@ucla.edu}{mpeter@ucla.edu}\\[0.4cm]

\noindent Subject: Airbus cover letter\\
Position name: Assitant Business Analyst\\
\vfill
Dear hiring manager,\\[0.8cm]

I am writing today to showcase three ways in which I would be a valuable asset to Airbus in the role of assistant business analyst.

Firstly, my previous experience in sales enabled me to secure initial funding for a simulation software designed for Airbus' numerical continuity problematic.

Secondly, I have an academic \& practical understanding of FPGA systems, having worked on such systems at the CERN's Large Hadron Collider.
During this experience, I designed a GUI prototype intended to replace all TUI previously used for measurement systems - a major upgrade within the CERN!

Thirdly, I speak English and French fluently, making me a polyvalent asset in multi-lingual teams.
My previous experiences in European professional environments enable me to collaborate effectively in a variety of environments.

The three reasons highlighted above lead me to consider the role of assistant business analyst at the very intersection of my experiences, education and passions. Beggining a career at Airbus. \\[0.8cm]

Thank you for your consideration thus far,\\[0.4cm]

Marius Peter

\end{document}
