\documentclass{letter}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{fourier}
% \usepackage{mathptmx}


\begin{document}

\signature{Marius Peter}
\longindentation=0pt
\address{Marius Peter\\
    11090 Strathmore Dr\\
    Los Angeles CA 90024
}


\begin{letter}{Attn: Moe Fakih\\
        VCA Green\\
        1845 W. Orangewood Ave, Suite 220\\
        Orange, CA 92868\\
        \bigskip
        \textbf{Subject:} VCA Green cover letter\\
        \textbf{Position:} Project Administrator
    }

    \opening{\vfill~Dear Mr. Fakih,}

    I am writing to showcase what I hope to contribute to VCA Green, as a project administrator. 

    After browsing VCA Green's current collaborators on LinkedIn, I saw that most recent hires start off as project administrators.
    I researched the type of responsibilities assigned to this role, and there is a compelling overlap between the latter and my background. 

    I successfully created a durable client relationship during my previous employment at Cosmo Tech.
    My responsiblities included surveying potential clients in the aerospace sector;
    after 3 months, I had secured funding from Airbus for an industrial process modellling software tailored to their industrial needs.
    As a result, I gained a much better understanding of the requirements elicitation process and built my confidence in client-facing situations. 

    Secondly, I was thrilled to obtain LEED GA certification this past March.
    Preparing for the examination confirmed my desire to apply my engineering education to promote public welfare in the most environnmentally sustainable way possible.

    Lastly, I developed a strong work ethic during my studies at UCLA and previous internships.
    I work in a timely fashion and display ongoing commitment to my clients' cases, in an effort to foster long-term, high-quality customer relationships.
    These are at the basis of a rock-solid branding -- and given VCA Green's current branding, I believe I could become a valuable collaborator. 

    The achievements I outline above lead me to consider a project administrator role at VCA Green at the very intersection of my experiences, education and passions.
    I am eager to get in touch in order to further discuss VCA Green's current needs.

    \closing{Thank you for your consideration,}

\end{letter}

\end{document}
