\documentclass{letter}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
% \usepackage{mathptmx}
\usepackage{setspace}
\usepackage{hyperref}


\newgeometry{margin=1in}

\signature{Marius Peter}
\address{11090 Strathmore Dr\\Los Angeles CA 90024\\USA}

\begin{document}

\begin{letter}{
\textbf{Subject:} Georgia Tech cover letter\\
\textbf{Position:} Model-Based Systems Engineer\\
}

\opening{Dear Hiring Manager,}

The MBSE engineer opening at the GTRI caught my attention because of the many transferrable skills I could contribute in this role.
Previously at Cosmo Tech, I developed my understanding of Model-Based Systems Engineering, UML and SysML; my responsiblities placed me at the forefront of our clients' requirements elicitation process. 

By the end of my employment at Cosmo Tech, I had contributed to selling Airbus a MBSE Decision Support Software tool designed specifically for their need.
Airbus wanted better visibility in the \textit{Final Assembly Line} stage of the A320 Neo manufacturing, because the increased complexity of this new aircraft made it very difficult to evaluate the impact of an upstream delay on the final assembly duration.

Following the initial contact with the Airbus team, I strived to understand their modeling workflow by downloading trial versions of the softwares they used (PolarSys Capella and SIMPROCESS), and modeling a typical \textit{FAL} environment;
then, I repeated the same exercise using Cosmo's in-house tools, as well as a competitor's product (AnyLogic).

During the next conference call with the Airbus team, I laid down the results of my benchmark and presented Cosmo's value proposition.
I connected our product's features with the requirements Airbus had elicited earlier, and showcased how our product best met their needs.
Airbus was thrilled by our efforts to understand their current workflow, and were rapidly convinced as to why they should buy Cosmo's solution over competing products.

This experience enabled me to better understand the end-to-end sales process, from lead generation till sale closure;
to improve my listening skills during the requirements elicitation phase;
and to further develop my understanding of Model-Based System Engineering in an industrial setting. 

The results I outline above lead me to consider the role of MBSE engineer at the very intersection of my experiences, education and passions.

\closing{Thank you for your consideration thus far,}

\end{letter}
\end{document}
